\documentclass[9pt]{developercv}

\begin{document}

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip}
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Kei}}}}}
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Palabasan}}}}}
	
	\vspace{6pt}
	
	{\huge Digital Design Engineer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.24\textwidth} 
	\vspace{-\baselineskip}
	\icon{At}{12}{\href{mailto:kei@silikeite.me}{kei@silikeite.me}}\\	
	\icon{Globe}{12}{\href{https://silikeite.me}{silikeite.me}}\\
	\icon{MapMarker}{12}{Diliman, Quezon City}\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} 
	\vspace{-\baselineskip}
	\icon{Github}{12}{\href{https://github.com/silikeite}{silikeite}}\\
	\icon{Linkedin}{12}{\href{https://linkedin.com/in/silikeite}{silikeite}}\\
	% \icon{Twitter}{12}{\href{https://twitter.com/silikeite}{@silikeite}}\\
\end{minipage}

\vspace{0.5cm}

\begin{minipage}[t]{0.475\textwidth} 
	\vspace{-\baselineskip}
	\cvsect{About me}

	Digital designer in Verilog with Linux driver experience and educational background in MEMS design and fabrication. \\

	\cvsect{Experience}

	\begin{entrylist}
		\entry
			{May 2022 \\ - \\ now}
			{\href{https://smartfoxdata.com}{Smartfox Data Solutions, Inc.}}
			{Hardware Engineer; Full-time Remote}
			{\
				- Underwent training in digital design and verification with Verilog and UVM, contributing to internal AXI-related IP. \\
				- Designed and tested FPGA-based chip testing equipment for various applications. \\
				- Adopted Agile methodologies and Gitflow, improving communication within the team and to product owners and stakeholders. \\
				- Developed Linux drivers for custom graphics hardware, enabling rendering and high-level testing of hardware designs on Xilinx FPGAs using industry-compatible APIs and benchmarks.
			}	
		% \entry
		% 	{2018-2022}
		% 	{Programming Consultant}
		% 	{Rizal National Science High School}
		% 	{
		% 		- Microcontroller and interface code programming for Robotics and Science Fair competitions.
		% 	}
	\end{entrylist}
	\cvsect{Organizations}
	\begin{entrylist}
		\entry
			{Oct 2021 \\ - \\ Oct 2022}
			{\href{https://upcrc.org}{UP Competitive Robotics Club}}
			{Chief Executive Officer}
			{Led the organization's post-pandemic transition from online to physical activities.\\
			- Managed UFM booth, driving a significant increase in recruitment, showing importance of F2F activities and interactive demos.\\
			- Handled first F2F robotics workshops, improving applicant and member retention.\\
			- Implemented necessary constitutional amendments and managed leadership elections to ensure organizational sustainability.}
		% \entry
		% 	{2020-2021}
		% 	{Chief of Tournament Operations}
		% 	{\href{https://upcrc.org}{UP Competitive Robotics Club}}
		% 	{Managed logistics and handling for the Tournament Organizing Workshop and Robotics Ideathon}
	\end{entrylist}


\end{minipage}
\hfill 
\begin{minipage}[t]{0.475\textwidth} 
	\vspace{-\baselineskip}

	\cvsect{Skills}

	\textbf{Teamwork/Communication:} Scrum, Agile, Team Management, LaTeX, Markdown

	\textbf{Languages:} C/C++, Verilog, SystemVerilog/UVM, GLSL, Python

	\textbf{OS/Applications:} Linux (systemd), Tensorflow, Vulkan, LTSpice, JAMStack

% 	\textbf{Miscellaneous:} Hardware/software troubleshooting and debugging, Linux system configuration and maintenance, problem-solving, team communication

	\cvsect{Education}
	
	\begin{entrylist}
		\entry
			{Aug 2019 \\ - \\ Aug 2023}
			{\href{https://www.eee.upd.edu.ph/undergraduate-programs/bs-electronics-and-communications-engineering}{BS Electronics Engineering}}
			{University of the Philippines Diliman - Quezon City, NCR}
			{Graduated \emph{summa cum laude} (1.12 GWA, equiv. 3.8 GPA)\\
			Affiliated with \href{https://www.up-microlab.org/}{UP Microlab for capstone project.}}
		% \entry
		% 	{2017-2019}
		% 	{Senior High School}
		% 	{Rizal National Science High School - Binangonan, Rizal}
		% 	{Academic Track, STEM Strand\\
		% 	Graduated with High Honors, Best in Science}
	\end{entrylist}
% 	\cvsect{Achievements}
% 	\begin{entrylist}
% 		% \entry
% 		% 	{2019}
% 		% 	{Synergy Software Solutions Competition}
% 		% 	{UP Diliman; National Level}
% 		% 	{1st Place}
% 		\entry
% 			{2018}
% 			{World Invention Creativity Olympiad}
% 			{Seoul, South Korea}
% 			{Gold Medal}
% 		\entry
% 			{2017}
% 			{World Invention Creativity Contest}
% 			{Seoul, South Korea}
% 			{Gold Medal, MyRIS Special Award}
% 		\entry
% 			{2016}
% 			{International Olympiad in Informatics}
% 			{Kazan, Russia}
% 			{Contestant}
% 		\entry
% 			{2015}
% 			{International Olympiad in Informatics}
% 			{Almaty, Kazakhstan}
% 			{Contestant}
% 	\end{entrylist}
	\cvsect{Publications}
	\begin{entrylist}
		\entry
			{2023}
			{FPGA-targeted optimization approaches for SVM and CNN human activity recognition models using the HARTH and HAR70+ datasetss}
			{Palabasan, K.R., Rajagopalan, R.S., Manzano, J.M., Rosales, M.D., De Leon, M.T., Hizon, J.R.E.}
			{Conference paper for PrimeASIA 2023. \\
			\href{https://dx.doi.org/10.1109/PRIMEAsia60757.2023.00009}{doi:10.1109/PRIMEAsia60757.2023.00009 }}
		\entry
			{2023}
			{Comparison of hardware-optimized CNN and SVM models for human activity recognition using the HARTH and HAR 70 + datasets}
			{Palabasan, K.R., Rajagopalan, R.S., Manzano, J.M., Rosales, M.D., De Leon, M.T., Hizon, J.R.E.}
			{Submitted as Undergraduate Project. Conference paper for ISOCC 2023. Furiosa AI Award. \\ \href{https://dx.doi.org/10.1109/isocc59558.2023.10396338}{doi:10.1109/isocc59558.2023.10396338 }}
		% \entry
		% 	{2018}
		% 	{Effectiveness of Anti-Overloading System for Automotive Transport (AOSAT) in Selected Truck Drivers in Binangonan Rizal}
		% 	{Otiong, K.SJ., Palabasan, K.R., Ramirez, J.C.B.}
		% 	{Submitted as Senior High School Thesis, Submitted for WICO 2018}
		% \entry
		% 	{2017}
		% 	{Breath Analyzer for Automotive Interlock}
		% 	{Palabasan, I.V.R., Ordonez, J.DJ., Aguinaldo, V.S.C.}
		% 	{Submitted for WICC 2017}
	\end{entrylist}
\end{minipage}

\vspace{0.5cm}

\begin{minipage}[t]{0.2\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Languages}

	\textbf{English} - native\\
	\textbf{Filipino} - proficient\\
	\textbf{Japanese} - proficient\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.6\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Interests}
	
	% 	Music, Singing, Guitar, Mechanical Keyboards, Anime and Manga, Cosplay, Programming, Amateur Radio, Robotics
	\textbf{Music} - JPop/Vocaloid/Alt (Yorushika, Nakiso, Kanaria); Singing, Guitar.\\ \textbf{Subculture} - Anime/Manga, Cosplay, VTubers. \\
	\textbf{Tech} - Custom Keyboards, AI model training/tweaking, Amateur Radio. \\
	\textbf{Games} - ARMA 3, Minecraft, GMod
\end{minipage}


\end{document}
